---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))

```{r}
library(rvest)
library(rgeizhals)

## naming conventions:
## * listpage, listpagehtml
## * detailpage, detailpagehtml

url_geizhals <- "https://geizhals.at/?cat=hwaeschtr&xf=1027_W%E4rmepumpentrockner%7E1296_10%7E1747_8%7E7641_40%7E7653_9"

## get html of url:
listpagehtml <- read_html(url_geizhals)

data.frame(
  prodname = get_product_names(listpagehtml),
  rating = get_ratings(listpagehtml),
  rating_n = get_ratings_n(listpagehtml),
  offers_n = get_offers_n(listpagehtml),
  detaipage_url = get_detailpage_urls(listpagehtml)
)

```

```{r}

## pick one detailpage:
detailpage <- get_detailpage_urls(listpagehtml)[1]

## get html of url:
detailpagehtml <- read_html(detailpage)

## just get categories (without values):
get_detailpage_categories(detailpagehtml)

## get categories and their values:
get_keyval_tbl(detailpagehtml)

## get prices (first page):
get_prices(detailpagehtml)

## get summary of prices (first page):
get_price_summary(detailpagehtml)


```

